---
title: "Rayshader Example"
author: "Joseph Randolph"
date: "11/19/2019"
output: html_document
---

Install and call packages
```{r}
install.packages('rayshader') # really cool pacjage that shows model images with layers of sading for elevations! 
library(rayshader)
#install.Rtools(TRUE)
#install.packages('devtools')
#devtools::install_github('tylermorganwall/rayshader')
```

We have to prepare 'tempfile' and 'tempmap' for arguments in the code below
```{r}
#Prepare 'tempfile' and 'tempmap' for arguments in the code below
tempfilename <-  tempfile()
png(tempfilename,width = 401,height=401)
tempmap = png::readPNG(tempfilename)
```

We use monteraybay elevation data to produce a basic topographical representation using a light source specifeid by the raysade() function with an overlay
```{r}
# 'montereybay' is a data set with in rayshader containng elevation data
montereybay <- montereybay
montereybay %>%
  ray_shade(zscale=50,maxsearch = 500,anglebreaks = seq(20,30,0.1)) %>%
  add_overlay(tempmap,alphalayer = 0.5) %>%# alphalayer is a 3-layer array, this argument tells which color is interpretted as completely transparent.
  plot_map()
```

We will add more funtions/layer to the map. This will create a shadow which will add moe contrast
```{r}
montereybay %>%
sphere_shade() %>% #sphere_shade also includes 7 built-in palettes: “imhof1”, “imhof2”, “imhof3”, imhof4“,”desert“,”bw“,”unicorn
add_overlay(tempmap,alphalayer = 0.4) %>% #this argument tells which color is interpretted as completely transparent
add_shadow(ray_shade(montereybay,zscale=50,maxsearch = 500)) %>%#adds shadow to a textured color array
plot_map()

```


```{r}
#produces  Ambient Occlusion Shadow Map (map with no light)
amb = ambient_shade(heightmap = montereybay)
plot_map(amb)
```


```{r}
#Create map of elevation indicated by color
montereybay %>%
  height_shade() %>%
  plot_map()

```

```{r}
#Add a shadow to previous map
montereybay %>%
  height_shade() %>%
  add_shadow(ray_shade(montereybay,zscale=50),0.3) %>%
  plot_map()
```

```{r}
#Change the palette
montereybay %>%
  height_shade(texture = topo.colors(256)) %>%
  add_shadow(ray_shade(montereybay,zscale=50),0.3) %>%
  plot_map()

```
 
 Here we will create a 3d color model and we will use render_snapshot() to pruce the image
```{r}
#creat a 3d model
montereybay %>%
  sphere_shade() %>%
  plot_3d(montereybay,zscale = 50, water = TRUE, waterlinecolor="white")
render_snapshot()

```


