---
title: "R Stats Package Exercise"
author: "Jerri Schorr"
date: "11-19-2019"
output: html_notebook
---

### Set Up 

We will start by downloading the package and putting our library in the set-up chunk below. Make sure you delete the hashtag before `install.packages` to install Stats Package.

Stats is a base package, meaning it should already be installed, if it is not or if it needs updated, R will do so when you run `install.packages`.

```{r setup, include=FALSE}
#install.packages("stats")
library(stats)
head(cars,5) #view first 5 rows of cars data set
```

* We will be using the "cars" data set in R for the following exercises

### Exercise 1

Let's find the median of data.

* The median is used instead of the mean when the data has a very large spread of data

```{r}
median(cars$speed)
median(cars$speed)
#you can choose any column, variable, or data set you would like to put in the function
```

### Exercise 2

Now let's find the standard deviation of data.

* Standard Deviation is a measure of spread.

```{r}
sd(cars$dist)
sdcars$speed)
#you can choose any column, variable, or data set you would like to put in the function
```


### Exercise 3

Now let's find the Inter Quartile Range (IQR) of data.

* The IQR tells you the distance between the 3rd quartile and the 1st quartile

```{r}
IQR(cars$speed)
IQR(cars$dist)
#you can choose any column, variable, or data set you would like to put in the function
```


### Exercise 4

Next we will fit the data with a Linear Model to see its relationship

* Linear Models show whether data is correlated in a positive direction, negative direction, or if there is no correlation.

```{r}
dist <- cars$dist
speed <- cars$speed
plot(dist, speed)
fit1 <- lm(speed ~ dist, data = cars)
abline(fit1, col = "red")
# be sure to highlight all code above and run all at once to plot the data and see the fir of the linear model
#you always want to put your response, or y, variable first in the lm function.
summary(fit1)# this will give you all of the details for the linear model 


plot(speed, dist)
fit2 <- lm(speed~ dist, data = cars)
abline(fit2, col = "red")

summary(fit2)
```





