---
title: "Lists"
---

```{r setup}
library(tidyverse)
install.packages("repurrrsive")
library(repurrrsive)
library(broom)
names(sw_people) <- sw_people %>% map_chr("name")

# Toy data
set.seed(1000)
exams <- list(
  student1 = round(runif(10, 50, 100)),
  student2 = round(runif(10, 50, 100)),
  student3 = round(runif(10, 50, 100)),
  student4 = round(runif(10, 50, 100)),
  student5 = round(runif(10, 50, 100))
)

extra_credit <- list(0, 0, 10, 10, 15)

names(who) <- str_replace(names(who), "newrel", "new_rel")
tb <-  
  who %>%
  gather("codes", "n", 5:60) %>%
  separate(codes, c("new", "type", "sexage"), sep = "_") %>%
  select(-new, -iso2, -iso3) %>%
  separate(sexage, c("sex", "age"), sep = 1) %>%
  drop_na(n)
```

# Lists

## Your Turn 1

Run the code below, which displays a list. What do you see?

```{r}
sw_people %>% head(3)
sw_people$`Luke Skywalker`
sw_people[[2]]
```

## Quiz

```{r}
vec <- c(-2, -1, 0)
lst <- list(-2, -1, 0)

abs(vec)
abs(lst) # error bc not a list
```

## Your Turn 2

Who was taller Anakin Skywalker or Darth Vader? 
Use the RStudio Viewer to find the answer (in cm).

*Hint: View() sw_people*

```{r}
sw_people$`Luke Skywalker` # [1] "172"
sw_people$`Anakin Skywalker` # [1] "188"
sw_people$`Darth Vader` # [1] "202"
# Darth Vader
```

## Your Turn 3

Here are two subsetting commands. Do they return the same values? Run the code chunks below to confirm.

```{r}
a_list <- list(num = c(8, 9), 
               log = TRUE,    
               cha = c("a", "b", "c"))
# think of a train
```

```{r}
a_list["num"]
```

```{r}
a_list[["num"]]
```
```{r}
sw_people[["Anakin Skywalker"]][["height"]] # prints height alone as [1] "188"
```


Take Aways

* Use `View()` to inspect lists
* Use `[[ ]]`, or `$` to extract values from lists
* Lists can be a column in a data frame
* Tables are an organizational structure that you can manipulate.
* Use fx to repeat processes that are done <3x
* Construct fx that have good names, that are simple & flexible
* Lists can contain multiple types of values
